---
title: "Normal Distribution"
author: "Sugyoo, Lee"
date: "7 March 2018"
output: ioslides_presentation 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Normal Distribution
Let's look at a function that generates an arbitrary number that follows a specific distribution, such as a normal distribution.

| Function|  Prefix  |Parameters|
|---|---|---|
|Density function| d  | dnorm(x, mean=0, sd=1)  |
|Cumulative distribution function   |p   | pnorm(q, mean=0, sd=1,lower.tail=TRUE/FALSE)|
|Quantile function   |q   |qnorm(p, mean=0, sd=1, lower.tail=TRUE/FALSE)|
|Random number generation  |r   |rnorm(n, mean=0, sd=1)|

## Density distribution plot
```{r}
x <- seq(-3, 3, length=200) 
plot(x, dnorm(x, mean=0, sd=1), type='l'
     , main="Normal distribution, X~N(0,1)")

```

## Cumulative normal distribution plot  
```{r }
x <- seq(-3, 3, length=200) 
plot(x, pnorm(x, mean=0, sd=1), type='l'
     , main="Cumulative normal distribution, X~N(0,1)")
```

## Calculate a cumulative function: pnorm
```{r }
pnorm(q=c(1), mean=0, sd=1)
pnorm(q=c(-1), mean=0, sd=1) 
pnorm(q=c(-2), mean=0, sd=1) 
```

## qnorm(p, mean=0, sd=1, lower.tail=TRUE/FALSE)
When you want to know the quantile q corresponding to a specific cumulative distribution function value p in a population that follows a normal distribution....
```{r}
pnorm(q=c(1), mean=0, sd=1)
qnorm(p=0.8413447, mean=0, sd=1, lower.tail = TRUE) 
qnorm(pnorm(1))
```

## Generation of randomly distributed numbers
```{r}
random_norm_100 <- rnorm(100, mean=0, sd=1)
random_norm_100
```

## And Histogram of random 100

```{r}
hist(random_norm_100)
```

